Rethinking Felony Disenfranchisement: The Case of New York City and Miami

### 2019-05-02 markdown/kmorris_thesis.Rmd
baby let me write write write write write

@@

#Method {-}

>>>>

#What This Paper Examines {-}
This paper begins by examining the effect of felony disenfranchisement in the New York City Mayoral election of 2017. This paper is primarily interested in whether felony disenfranchisement has impacts on local political distribution. If, for instance, voters in particular marked neighborhoods turnout at lower rates because of disenfranchisement policies, this could have ramifications for city-wide policy. @Martin2013, for instance, documents the relationship between voter turnout and the responsiveness of Congressional representatives. "[H]igher citizen participation is rewarded," they argue, "with enhanced policy responsiveness." If the neighborhoods most impacted by felony disenfranchisement turn out at lower rates, they may find that their elected representatives are less likely to support their needs.

Although research on the impact of local turnout on city-wide policy is scarce, @Anzia2019 examines the impact of senior turnout on "senior-friendly" policy at the city level. Anzia does not find that senior turnout in general increases the likelihood of senior-friendly policies, but that elected officials *are* responsive to senior turnout when seniors "are a more cohesive, meaningful group." American cities are highly segregated by race and by class, but less so by age. As such, Anzia's study does not speak directly to the impact of *neighborhood* turnout rates on city policy. An extension of her paper, however, implies that what she finds might be probitive to the effect of neighborhood turnout rates. Insofar as neighborhoods vote cohesively on issues such as school and park funding, their turnout rates may influence city policy.

@@

##Geocoding {-}
Voters' home addresses were converted to latitudes and longitudes using a geocoder provided by SmartyStreets. These latitudes and longitudes were then converted to census block groups using the statistical program R and shapefiles available from the United States Census Bureau.

#Matching Methodology {-}
In order to estimate the impact of felony disenfranchisement at the neighborhood level, I begin by indentifying voters who were inelibile to cast a ballot in the 2017 mayoral election in New York City. In order to identify incarcerated and paroled voters, matching records from the Department of Corrections and the Voter File is necessary. I here use the methodology first developed by Burch [-@Burch2010; -@Burch2011]. I use first, middle, and last names, and dates of birth, to join these two datasets.^[Matching on first and last names and dates of birth can result in false positive matches, especially in large states like New York. Following @Meredith2013, I report estimates of the potential impact of these false positives in the Appendix.]
